Multispecies survey specifications

### 2020-11-05 msSurveysTest.Rmd
plot new surveys--not yet run

>>>>

```{r read-newsurvs}

# source(here("config", "NOBA2config.R"))
# omlist_ss <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))
# source(here("config/omdimensions.R"))

# add this paste0(d.name, "/mscensus1") and add option to name save directory in wrappers
survObsBiom <- read_savedsurvs(d.name, 'survB')
age_comp_data <- read_savedsurvs(d.name, 'survAge')
len_comp_data <- read_savedsurvs(d.name, 'survLen')
wtage <- read_savedsurvs(d.name, 'survWtage')
annage_comp_data <- read_savedsurvs(d.name, 'survAnnAge')
annage_wtage <- read_savedsurvs(d.name, 'survAnnWtage')

catchbio_ss <- readRDS(file.path(d.name, paste0(scenario.name, "fishCatch.rds")))
catchbio_ss <- catchbio_ss[[1]] #in same time unit as surveys

fish_age_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsAgeComp.rds")))
fish_age_comp <- fish_age_comp[[1]]

fish_len_comp_data <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsLenComp.rds")))

fishwtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsWtAtAge.rds")))
fishwtage <- fishwtage[[1]] #need to change time units?

fish_annage_comp <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullAgeComp.rds")))
fish_annage_comp <- fish_annage_comp[[1]]

fish_annage_wtage <- readRDS(file.path(d.name, paste0(scenario.name, "fishObsFullWtAtAge.rds")))
fish_annage_wtage <- fish_annage_wtage[[1]] #need to change time units?

### Visualize surveys with different q and selectivity {.tabset #census}

We are using the full time series for biomass and weight at age, and a subsample of years 30-53 for compositions. In this test we see the effect of survey efficiency and selectivity as well as the effect of surveying in one season. (Observation error that differs by species group is included in the survey biomass time series.) Samples for length and age assume a total of 10000 fish were randomly sampled for each species in each survey (surveffN defined in the survey config files).

### Visualize fisheries observed with some error {.tabset}

Here we are not sampling all fished areas, and the observation error on the total catch index is higher. We are using the full time series for total catch and weight at age, and a subsample of years 30-35 for compositions. Fishery length and age composition is sampled every output timestep. Fishery effN for length and age sampling was 1000 fish per year (200 per time step), so this is reflected in the composition plots.
